How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-14 analysis/paper/paper.Rmd
test to push
deleted individual plot for spd models

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the critical envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit, with the next-best fit (exponential) having a higher AIC score by a minor margin at -48.6."}
source(here::here("analysis/paper/008-summed-probability-distributions.R"))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```

@@

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->

>>>>

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the critical envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit, with the next-best fit (exponential) having a higher AIC score by a minor margin at -48.6."}
quietly(source(here::here("analysis/paper/008-summed-probability-distributions.R")))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```

@@

<!--The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
